Scalar on Function Regression

### 2022-01-06 Presentation/slides.tex
Increment

	\begin{frame}{Theory}
		A simple functional dataset is given by 
		$$\{x_{i}(t_{j,i}) \in \mathbb{R} \: \vert \:  t_{j,n} \in [T_1, T_2], \; i = 1,2,...,N, \; j = 1,2,..., J_i  \}$$

>>>>

	\begin{frame}{Theory}
		A simple functional dataset is given by 
		$$\{x_{i}(t_{j,i}) \in \mathbb{R} \: \vert \: i = 1,2,...,N, \; j = 1,2,..., J_i, \; t_{j,i} \in [T_1, T_2] \}$$
